\documentclass{article}

\usepackage[margin=2.5cm,left=2cm,includefoot]{geometry}
\usepackage{hyperref}
\usepackage{array}
\usepackage{enumitem}
\usepackage{graphicx}

% Header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}

\rhead{COS301 - Software Engineering}
\lhead{Broadsword}
\fancyfoot{}
\fancyfoot[R]{Page \thepage}

\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{1pt}
%

\begin{document}

	\begin{titlepage}
		\begin{center}

			\line(1,0){400}\\
			[6mm]
			\huge{
				\bfseries NavUP Broadsword\\
				\bfseries Implementation Documentation
			}\\
			[2mm]
			\line(1,0){400}\\
			[15mm]
			\textsc{\large{\textbf{NavUP}}}\\
			[4.5mm]
			\textsc{\large University of Pretoria - Broadsword}\\
			[20mm]
			\large{\textbf{Created By:}}\\
			[2mm]
			\large{
				\href{https://github.com/TheZimbo16/COS301-Broadsword-Users}{Team Broadsword-Users}\\
				\href{https://github.com/wanrick/bsword-notification}{Team Broadsword-Notifications}\\
				\href{https://github.com/lyle-univ/cos301-broadsword-data}{Team Broadsword-Data}\\
				\href{https://github.com/sjohandup/SE_BroadSword-GIS}{Team Broadsword-GIS}\\
				\href{https://github.com/AndriesJacobus/COS301Phase3BroadswordNavigation}{Team Broadsword-Navigation}\\
				\href{https://github.com/KeatonPennels/COS-301-Broadsword-Access}{Team Broadsword-Access}\\
				\href{https://github.com/Regan-Koopmans/NavUP-Broadsword}{Team Broadsword-Integration}
			}\\
			[30mm]
			
		\textsc{\Large NavUP Broadsword GitHub Repository}\\[2mm]
			To view the repository, please click 
		\href{https://github.com/Regan-Koopmans/NavUP-Broadsword}{\textbf{here}}. \\[35mm]
		\end{center}
		\begin{flushright}
			\textsc{\large April 2017}
		\end{flushright}
	\end{titlepage}

	\cleardoublepage
	\thispagestyle{empty}
	\tableofcontents
	\cleardoublepage

	\thispagestyle{empty}
	\listoffigures
	\cleardoublepage
	\setcounter{page}{1}
	
	\section{Introduction}\label{sec:intro}
		This chapter of the document aims to give a description as well as an overview of the content of this document. The content of this document pertains to the implementation phase of the Broadsword instance for the NavUP system.		
		
		\subsection{Purpose}\label{sec:intro-purpose}
		The purpose of this document is to explicitly provide the documentation generated during the implementation phase of the Broadsword NavUP instance. The documentation is intended to give a detailed breakdown of the inner-workings of the respective modules that were implemented.
		
		\subsection{Scope}\label{sec:intro-scope}
		This document will only delve into the documentation generated by the Broadsword instance of the NavUP system. All the documentation that is required or deemed to be necessary will be discussed by the various implementation teams. The documentation represented will be that which is viewed in isolation with respect to the various teams or modules, and will represent how the various teams viewed it within their specific contexts. This emphasises the modularity of the implemented system.
		
		
		\subsection{Overview}\label{sec:intro-overview}
		All subsequent sections will headline the various modules that were developed during the implementation phase. Each of these sections will provide a detailed breakdown of the respective modules. The modules are sorted alphabetically and are as follows: Access, Data, GIS, Navigation, Notifications and Users.
	
		
	\clearpage
		
	\section{Access module}\label{sec:access}

		
		
	\clearpage

	\section{Data module}\label{sec:data}
	
		

	\clearpage
	
	\section{GIS module}\label{sec:gis}
	
			

	\clearpage
	
	\section{Navigation module}\label{sec:navigation}
	
	
	
	\clearpage
	
	\section{Notifications module}\label{sec:notification}
	
	
	
	\clearpage
	
	\section{Users module}\label{sec:users}
	
	

\end{document}
